A Comparison of Parallel Graph Processing Implementations

### 2017-05-11 papers/publication/paper-pollard.tex
minor edits

To address these issues, we present \emph{easy-parallel-graph\mbox{-\textasteriskcentered}}
% Here, \textasteriskcentered\ could be \emph{processing}, \emph{performance-analysis}, or \emph{algorithm-comparison})
\footnote{Available at \url{https://github.com/HPCL/easy-parallel-graph}}, a utility which simplifies the installation, comparison, and performance analysis of the three most widely implemented graph algorithm building blocks: breadth first search (BFS), single source shortest paths (SSSP), and PageRank (PR). With this tool we select a small number of graph processing libraries over which we homogenize all aspects of execution to fairly compare performance. Additionally, we present an example use of this framework to analyze the performance, energy consumption, and scalability of specific algorithm implementation. This enables algorithm designers to select high performance reference implementations with which they can compare their improvements. To be clear, we are not proposing a new benchmark suite or providing any reference implementations. We introduce a framework for detailed and fair comparison of existing graph software packages without requiring the user to be familiar with them.

@@

\section{Methodology}
\todo[inline]{Start with dataset subsection, write new intro to methodology, move this into inputs. We're comparing algorithms not applications. Understand those since they're the building blocks. Not comparing architectural details (cite that Nai paper). Important paragraph.}
Our utility is broken down into five principal phases indicated in \figurename~\ref{fig:epg-overview}, each of which requires no more than a single shell command. The five phases are as follows:
\begin{enumerate}
	\item Installing modified, stable forks of each software package to ensure homogeneity.
	\item Given a synthetic problem size or a real-world graph file, generate the files necessary to run each software package.
	\item Given a graph and the number of threads, run each algorithm using each software package multiple times.
	\item Parse through the log files to compress the output into a CSV.
	\item Analyze the data using the provided R scripts to generate plots.
\end{enumerate}

@@

\subsection{Parsing and Data Analysis}
Our example analyzes data using the R programming language and shell scripting parsers. The example workflow provided in our utility yields the figures generated in this paper.

>>>>

To address these issues, we present \emph{easy-parallel-graph\mbox{-\textasteriskcentered}}
% Here, \textasteriskcentered\ could be \emph{processing}, \emph{performance-analysis}, or \emph{algorithm-comparison})
\footnote{Available at \url{https://github.com/HPCL/easy-parallel-graph}}, a framework which simplifies the installation, comparison, and performance analysis of the three most widely implemented graph algorithm building blocks: breadth first search (BFS), single source shortest paths (SSSP), and PageRank (PR). With this tool we select a small number of graph processing libraries over which we homogenize all aspects of execution to fairly compare performance. Additionally, we present an example use of this framework to analyze the performance, energy consumption, and scalability of specific algorithm implementation. This enables algorithm designers to select high performance reference implementations with which they can compare their improvements. To be clear, we are not proposing a new benchmark suite or providing any reference implementations. We introduce a framework for detailed and fair comparison of existing graph software packages without requiring the user to be familiar with them.

@@

\section{Methodology}
\todo[inline]{Start with dataset subsection, write new intro to methodology, move this into inputs. We're comparing algorithms not applications. Understand those since they're the building blocks. Not comparing architectural details (cite that Nai paper). Important paragraph.}
Our framework breaks the process of characterizing performance into five principal phases shown in \figurename~\ref{fig:epg-overview}, each of which requires no more than a single shell command. The five phases are as follows.
\begin{enumerate}
	\item Installing modified, stable forks of each software package to ensure homogeneity.
	\item Given a synthetic problem size or a real-world graph file, generate the files necessary to run each software package.
	\item Given a graph and the number of threads, run each algorithm using each software package multiple times.
	\item Parse through the log files to compress the output into a CSV.
	\item Analyze the data using the provided R scripts to generate plots.
\end{enumerate}

@@

\subsection{Parsing and Data Analysis}
Our example analyzes data using the R programming language and shell scripting parsers. The example workflow provided in our framework yields the figures generated in this paper.
